Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to abstract 14/5/2019 12:06

\begin{abstract}
% We do not say this project, is more like: In this paoer an evolutionary ... 
% is presented or In this paper we present a .... (in third or first person plural) - MG   
This project consisted in the generation of an evolutionary computation-based
system capable to generate and evolve the structures of which one level of the
Angry Birds game is composed, these structures are evaluated according to the
stability of the structure as well as for the complexity of said structure.
% This is not true any more. Also the evaluation of the level is not the most
% important aspect - MG

For this a level generation system was designed based on the data obtained from
the game, said data consist in the number and type of pieces that appear and the
applied gravity of the game, the individuals of the group are evaluated by a
simulation of the generated level and then checking how the structures are
affected by the gravity of the game.  % This is not what the systems does any more
% It seems like you are describing Laura's work - M

The evolutionary computation system has the main objective of generating
structures based on the existent pieces of the game and evolving said pieces by
combining them in a process that simulates the rules of the Open-Ended Evolution
algorithm in which the evolution of this compounds is not inclined towards a
numeric objective rather than to extend the diversity from which the pieces may
be selected for a level.

@@

In the videogame industry many developers use a PCG style software that produces
raw images and designs used by other personnel to improve it and use it in order
to reduce the development cycles, and the productions cost. PCG as six focus
areas listed below:
% Jaime, you must add references to EVERY THING READ alsewhere : 
% We do not proposed this list, please add a reference. - MG

\begin{itemize}
    \item Level Design: This aspect involves only the design of specific
    sections of a game, primarily those in which the player is able to interact.
    \item Audio: This aspect is focused on designing soundtracks that are able
    to react to a player specific action.
    \item Visuals: This area is focused on creating or improving visual
    representations of objects on games, such as giving raw designs of players
    faces or improving the images of other graphics.
    \item Narrative: This aspect is focused on the generation of readable and
    coherent stories or plotlines of games.
    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on
    which a game is based by trying to play as a human would in order to improve
    said mechanics.
    \item Game Design: This aspect is focused on generating the rulesets and 
    mechanics of a new game. \cite{Yannakakis2017,Smith2014,shaker2016procedural}
    % The references are in this last item of the list JS
\end{itemize}

Furthermore we use genetic algorithms which is a method developed by 
John Holland on 1975 \cite{Holland1975} the genetic
algorithm (GA) is an optimization and search technique based on the principles
of genetic and natural selection, it allows a population composed of many
individuals, which by themselves represent a possible solution to the problem,
to evolve under specific selection rules in order to obtain the maximum fitness.

In other words a genetic algorithm is a method to solve optimization problems by
creating a population that will represent a possible solution and repeatedly
doing genetic operations as selection, crossover and mutation on each member of
the population in order to generate children for the next
generation that would be closer to the best solution of the problem, 
the cycles in this method where the operations are made are called
generations and by moving over this the population “evolves” or in other words,
they get closer to the best possible solution  to a specific problem.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=90mm]{Images/ga_life_cycle.png}}
    \caption{Life cycle of a genetic algorithm.}
    \label{algorithm_model}
\end{figure}

% Maybe this is well known, again our implementation is what we need to describe 
% JJ, what you think?

The main life cycle of a genetic algorithm shown on figure \ref{algorithm_model}
is described as follows:
\begin{enumerate}
    \item Initialize a random n population of values suitable for the solution.
    \item Evaluate the fitness of each individual (solution) in the population.
    \item Check if the stopping criteria has been met.
    \item If not.
    \begin{enumerate}
        \item Introduce new individuals to the population by crossover
        operations.
        \item Mutate a random value of the new individuals.
        \item Select new cross over individuals according to their fitness for
        the next generation.
    \end{enumerate}
    \item Loop from step 2 until an end condition is satisfied.
    \item Select the best individual of the population as the solution for the
    problem
\end{enumerate}

>>>>

\begin{abstract}
% We do not say this project, is more like: In this paoer an evolutionary ... 
% is presented or In this paper we present a .... (in third or first person plural) - MG   
In this paper an evolutionary computation-based system is proposed to generate 
levels for the angry birds video game, the levels themselves are composed of a 
set of birds that the player can use, a set amount of pigs that must be destroyed 
in order to progress to the next level and a given number of pieces that conform 
structures that may or may not protect the pigs from the player, this level 
generation system can create composites of pieces in order to create structures 
that can be used in the game this is based on our own interpretation of a open-ended 
evolutionary algorithm in which the evolution of the elements is not guided towards 
a single objective but rather is free to evolve and generate novelty or diversity 
in this case diversity of structures which the system can later select composites 
from in order to decide what will confomr a level, this data is saved in groups that represent a population 
that can evolve by an evolutionary algorithm in order to create more complex levels.
 This elements of a population are then evaluated by how complex they become and how 
 different they are from the rest of the group in order to create a variety of possible 
 levels to be played.

@@

In the videogame industry many developers use a PCG style software that produces
raw images and designs used by other personnel to improve it and use it in order
to reduce the development cycles, and the productions cost. 
PCG as various focus areas that resolve around a video game, however in this paper 
the main focus is the \textit{Level design} area which as the objective to design 
the different areas of a game in wich a player can interact with, since in the 
angry birds video game a level is represented by a scene then the system will 
have to create the entities (birds and pigs) and objects (pieces) in it in order 
to create a playable level.
